\begin{rubric}{Work Experiences}

\entry*[Apr. 2025 -- Present]%
	\textbf{PL/SQL Developer | Oracle Developer} 
    \par \emph{Tosan Company (Banking and Payment Solutions Provider), Iran}
    \par Analysis, design, and implementation of business applications using Oracle Relational Database Management System (RDBMS). Demonstrated expertise in logical and physical data modeling using normalization techniques. Created and optimized database objects including Tables, Views, Constraints, and Indexes (B-Tree, Bitmap, and Function-Based). Developed complex database components such as Stored Procedures, Functions, Packages, and Triggers using SQL and PL/SQL. Built sophisticated queries including hierarchical queries utilizing set operators and analytic functions (Ranking, Window functions). Leveraged REF cursors and collections for efficient data access from complex multi-table joins, ensuring optimal performance in high-transaction banking environments.
%
\entry*[Dec. 2023 -- Dec. 2024]%
	\textbf{Data Analyst and Machine Learning Engineer} 
    \par \emph{Freelancer}
    \par Engaged in diverse data analysis and machine learning projects, providing actionable insights and developing models for business optimization. Collaborated with the Football 360 technical team, applying machine learning algorithms to analyze performance data, develop predictive models, and generate visualizations to support strategic decisions.
%
\entry*[Dec. 2020 -- Dec. 2023]%
	\textbf{Researcher and Developer Engineer } 
    \par \emph{Entekhab Industrial Group, Isfahan, Iran}
    \par Led testing and certification processes in the Electrical Safety Laboratory, ensuring compliance with national and international standards. Contributed to securing export certifications in collaboration with global labs like SGS, Intertek, IMQ, and VDE. Supported ISO/IEC 17025 compliance, audits, and uncertainty analysis to ensure product safety and reliability.
%
\entry*[Nov. 2017 -- Apr. 2020]%
	\textbf{Research Assistant} 
    \par \emph{Electrical Engineering Dep., Sharif University of Technology, Tehran, Iran}
    \par Researched decentralized energy management and applied game theory to model energy markets, contributing to academic publications.
%
\entry*[Nov. 2017 --Nov. 2019]%
	\textbf{Teaching Assistant}
    \par \emph{Electrical Engineering Dep., Sharif University of Technology, Tehran, Iran}
    \par Guided students in the Linear Control lab with simulations, graded assignments and exams, and provided individual support to reinforce their understanding of control concepts.
\end{rubric}