\begin{rubric}{Relevant Academic \& Technical Projects}
\entry*%
	\textbf{Database Performance Optimization for Banking Systems} 
    \par \emph{Tosan Intelligent Data Miners Co., 2025}
    \par Designed and implemented high-performance database solutions handling millions of transactions. Optimized complex queries achieving 40\% performance improvement through advanced indexing strategies and query refactoring. Developed reusable PL/SQL packages for data processing pipelines.
%
\entry*%
	\textbf{Football Analytics and Performance Prediction System} 
    \par \emph{Football 360 Technical Team, 2024}
    \par Built machine learning models for player performance prediction and match outcome analysis. Developed interactive dashboards using Python and visualization libraries. Applied statistical methods for feature engineering and model validation, achieving 85\% prediction accuracy.
%
\entry*%
	\textbf{Optimal Mechanism Design for Product Allocation in Battery Company} 
    \par \emph{Game Theory Course, Sharif University of Technology, 2018}
    \par Developed MATLAB-based optimization mechanism for revenue maximization through efficient product allocation. Applied game-theoretic principles and mathematical modeling to solve multi-agent decision problems.
%
\entry*
	\textbf{Development of Numerical Optimization Algorithms}
    \par \emph{Numerical Optimization Course, Sharif University of Technology, 2018}
    \par Implemented advanced optimization algorithms from scratch in MATLAB, including Golden Section Search, Steepest Descent, Newton's Method, and BFGS. Demonstrated proficiency in algorithm design, numerical methods, and computational complexity analysis.
%
\end{rubric}
